SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-02-06 paper_rl/paper.tex
Add computational complexity

\begin{enumerate}
%\item \textbf{choose optimally}, taking only the data that contain the most information and skip the less relevant ones.
% Fares:
\item \textbf{choose optimally}, taking only samples that contain the most information and skip the less relevant ones.
\item have a parameter that allows to \textbf{trade off} classification performance for sparsity (choosing fewer packets).
\item be \textbf{independent of the classifier} so that any classifier can be used and that the classifier doesn't have to be aware of the sampling strategy.
\item be \textbf{retrainable} so that the sampling can be continuously adapted depending on the current threat landscape.
\item be able to \textbf{skip arbitrarily} many packets since network flows can be very long but only the first couple of packets are needed to decide whether an attack occurred or not and the remaining packets can be skipped altogether.
\end{enumerate}

@@

% Fares:
For this purpose we develop an \gls{rl}-based \gls{ids}: \textit{\ours{}} that fulfills the above properties. We show that a significant number of packets can be skipped while the accuracy does not drop
considerably. Compared to other common sampling techniques, \ours{} performs better when being trained on the same number of packets.

@@

@@

% Max: 1/4 is already pronounced one fourth
We show that the \gls{rl}-based approach with a tradeoff between classification accuracy and sparsity indeed results in higher sparsity the larger the tradeoff parameter, while potentially classification performance is sacrificed. Surprisingly, we saw that \ours{} on average chooses very few packets per flow: Typically $\approx \frac{1}{4}$. Furthermore, our results showed that \gls{rl}-based sampling can intelligently choose relevant packets for intrusion detection and outperform non-smart sampling techniques.

>>>>

\begin{enumerate}
%\item \textbf{choose optimally}, taking only the data that contain the most information and skip the less relevant ones.
% Fares:
\item \textbf{choose optimally}, taking only samples that contain the most information and skip the less relevant ones.
\item have a parameter that allows to \textbf{trade off} classification performance for sparsity (choosing fewer packets).
\item be \textbf{independent of the classifier} so that any classifier can be used and that the classifier doesn't have to be aware of the sampling strategy.
\item be \textbf{retrainable} so that the sampling can be continuously adapted depending on the current threat landscape.
\item be able to \textbf{skip arbitrarily} many packets since network flows can be very long but only the first couple of packets are needed to decide whether an attack occurred or not and the remaining packets be lightweight, so that computation efficiency is not lower because of the sampling overhead. 
\end{enumerate}

@@

% Fares:
For this purpose we develop an \gls{rl}-based \gls{ids}: \textit{\ours{}} that fulfills the above properties. We show that a significant number of packets can be skipped while the accuracy does not drop
considerably. Compared to other common sampling techniques, \ours{} performs better when being trained on the same number of flows.

@@

To make \ours{} as lightweight as possible, our implementation allows to let the sampling and the classifier to be implemented in the same neural network, meaning that no overhead is introduced. Without this option enabled, the computational power required is $2\times$ what would be required without the sampling. Thus, for this option, less than $50\%$ of packets must be sampled to gain a computational efficiency advantage.

@@

% Max: 1/4 is already pronounced one fourth
We showed that the \gls{rl}-based approach with a tradeoff between classification accuracy and sparsity indeed results in higher sparsity the larger the tradeoff parameter, while potentially classification performance is sacrificed. Surprisingly, we saw that \ours{} on average chooses very few packets per flow: Typically $\approx \frac{1}{4}$. Furthermore, our results showed that \gls{rl}-based sampling can intelligently choose relevant packets for intrusion detection and outperform non-smart sampling techniques.
